---
title: ""
author: "Adam Azoulay"
date: "November 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Leaflet Project (November 21st, 2018)

For this project, I decided to map the locations of the hometowns of all players from the Toronto Maple Leafs, an NHL hockey team. First we need to find a list of all active members on the roster. The most recent list is located on Wikipedia [here](https://en.wikipedia.org/wiki/Template:Toronto_Maple_Leafs_roster).

Let's go through the list and adding all the details to a data frame, in alphabetical order.

```{r}
df <- data.frame(lat = c(56.138611, 43.7, 44.05, 53.533333,
                         44.983333, 45.583333, 41.764167,
                         44.915537, 43.7, 60.674722, 42.9837,
                         62.8925, 44.3, 64.883333, 48.716667,
                         50.288056, 43.876667, 37.78, 34.189444,
                         55.82036, 49.366667, 41.892222, 43.6,
                         55.75),
                 lon = c(8.989722, -79.4, -79.466667, -113.5,
                         -93.266667, -73.75, -72.4375, -93.589409,
                         -79.4, 17.141667, -81.2497, 27.678333,
                         -79.583333, 20.8, 21.25, -107.793889,
                         -79.263333, -121.978056, -118.875,
                         37.33017, -123.166667, -87.943889,
                         -79.65, 37.616667))
playerNames <-  c("Frederik Andersen", "Connor Brown",
                  "Travis Dermott", "Tyler Ennis",
                  "Jake Gardiner", "Frederik Gauthier",
                  "Ron Hainsey", "Justin Holl", "Zach Hyman",
                  "Andreas Johnsson", "Nazem Kadri",
                  "Kasperi Kapanen", "Josh Leivo", 
                  "Par Lindholm", "Martin Marincin",
                  "Patrick Marleau", "Mitch Marner", 
                  "Auston Matthews", "Trevor Moore", 
                  "Igor Ozhiganov", "Morgan Rielly",
                  "Garret Sparks", "John Tavares",
                  "Nikita Zaitsev")
```

``` {r, echo = FALSE}
library(leaflet)
df %>% 
    leaflet() %>% 
    addTiles() %>% 
    addMarkers(popup = playerNames, clusterOptions = markerClusterOptions())
```

We can see the majority come from North America, and Canada in particular.